Analysis PPM-S

### 2020-04-10 production/prod_analysis-cfa.rmd
update-1004-2020

---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

This section, documents all the procedures related to the data analysis and measurement models.
(description)

@@

Design: this wave ....

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.Rmd",output_format = "html_document")
```

@@

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

**Load data**
```{r}
data01 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola1.sav",verbose = FALSE)

dat01 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv01"))   %>% na.omit()
dat02 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv02"))   %>% na.omit()
dat03 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv03_p")) %>% na.omit()

@@

dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
```

@@

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Percepción talento       | Perception talent      |
| 3. Percepción familia rica  | Perception rich family |
| 4. Percepción redes         | Perception networks    |
| 5. Preferencia esfuerzo     | Preference effort      |
| 6. Preferencia talento      | Preference talent      |
| 7. Preferencia familia rica | Preference rich family |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 01: Fixed order by perception

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))

@@

```{r correlacion v01}
cor01<-polychoric(dat01)
rownames(cor01$rho) <- c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor01$rho) <- c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r}
model01 <- 'perc_merit=~meritv01_perc_effort+meritv01_perc_talent
            perc_nmerit=~meritv01_perc_wpart+meritv01_perc_netw
            pref_merit=~meritv01_pref_effort+meritv01_pref_talent
            pref_nmerit=~meritv01_pref_wpart+meritv01_pref_netw'

@@

fit1_o <- cfa(model = model01,data = dat01,
            ordered = c("meritv01_perc_effort","meritv01_perc_talent",
                        "meritv01_perc_wpart","meritv01_perc_netw",
                        "meritv01_pref_effort","meritv01_pref_talent",
                        "meritv01_pref_wpart","meritv01_pref_netw"))

@@

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Preferencia esfuerzo     | Preference effort      |
| 3. Percepción talento       | Perception talent      |
| 4. Preferencia talento      | Preference talent      |
| 5. Percepción familia rica  | Perception rich family |
| 6. Preferencia familia rica | Preference rich family |
| 7. Percepción redes         | Perception networks    |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 02: Fixed order, by topic.

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort","2. pf.effort","3. pc.talent","4. pf.talent","5. pc.wpart","6. pf.wpart","7. pc.netw","8 pc.netw"))
```

```{r}
cor02<-polychoric(dat02)
rownames(cor02$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor02$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor02$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model02 <- 'perc_merit=~meritv02_perc_effort+meritv02_perc_talent
            perc_nmerit=~meritv02_perc_wpart+meritv02_perc_netw
            pref_merit=~meritv02_pref_effort+meritv02_pref_talent
            pref_nmerit=~meritv02_pref_wpart+meritv02_pref_netw'

@@

fit2_o <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                       "meritv02_perc_wpart"  ,"meritv02_perc_netw",
                                                       "meritv02_pref_effort" ,"meritv02_pref_talent",
                                                       "meritv02_pref_wpart"  ,"meritv02_pref_netw"))

@@

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor03<-polychoric(dat03)
rownames(cor03$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor03$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor03$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

fit3_o <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                       "meritv03_perc_wpart","meritv03_perc_netw",
                                                       "meritv03_pref_effort","meritv03_pref_talent",
                                                       "meritv03_pref_wpart","meritv03_pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

@@

```{r,results='hold'}
model03.tau <- '
perc_merit=~ r1*meritv03_perc_effort+r1*meritv03_perc_talent 
perc_nmerit=~r2*meritv03_perc_wpart+ r2*meritv03_perc_netw  
pref_merit=~ r3*meritv03_pref_effort+r3*meritv03_pref_talent 
pref_nmerit=~r4*meritv03_pref_wpart+ r4*meritv03_pref_netw'

@@

fit3_o.tau <- cfa(model = model03.tau,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                               "meritv03_perc_wpart","meritv03_perc_netw",
                                                               "meritv03_pref_effort","meritv03_pref_talent",
                                                               "meritv03_pref_wpart","meritv03_pref_netw"), std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c.tau ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o.tau) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

@@

```{r echo=FALSE,results='asis'}
stargazer(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw),
          type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor04$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

# Summary fit indices wave 01

```{r}
sum_fit<- bind_rows(fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
sum_fit$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fit$est <- c("Continous","Ordinal","Continous","Ordinal","Continous","Ordinal","Continous","Ordinal")
sum_fit <- select(sum_fit,mod,est,everything())

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01") %>%     kable_styling(full_width = F)  %>% 
      collapse_rows(columns = 1,valign = "middle")  %>%  
      footnote(number = c("Model 1: fixed order by percepction/preference", 
                          "Model 2: fixed order by topic (i.e: effort)", 
                          "Model 3: Randomized order",
                          "Model 4: Complete sample"));sumtable01

@@

```{r echo=FALSE,results='asis'}
stargazer(w02con,type = "html",          
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r echo=FALSE,results='asis'}
stargazer(w02pob,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r echo=FALSE,results='asis'}
stargazer(w02des,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

@@

```{r}
sum_fitw02<- bind_rows(fitmeasures(fitw02a_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02a_o)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_o)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_c)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_o)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],)

sum_fitw02$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fitw02$est <- c("Continuous","Ordinal","Continuous","Ordinal","Continuous","Ordinal","Continuous","Ordinal")
sum_fitw02 <- select(sum_fitw02,mod,est,everything())

kable(sum_fitw02,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 02") %>% 
  kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1,valign = "middle") %>% 
  footnote(number = c("Model 1: Control group sample", 
                      "Model 2: Poverty treatment condition sample",
                      "Model 3: Inequality treatment condition sample",
                      "Model 4: Complete sample"))
```

>>>>

---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

@@

On the first wave of the study we conducted the application of the Perceptions and Preferences Meritocracy Scale (PPM-S), in which we decided to test three different modalities for the application of the scale. The design of the study considered a sample of 2200 cases in Chile, using quotas for sex, age and educational level. The most important feature of this study consists in that we randomly assigned the participants to three different groups, in which the subjects complete one of the three combination of the questions. The key feature of these combinations relies on the display order of the questions regarding to each indicator of the scale. On this respect, we have three subsamples that correspond to each application modality that can be analysed separately, but also all together as a full sample.

The scale has eight indicators, divided in four questions for perception and four for preferences, which are also divided in meritocratic and non-meritocratic. The meritocratic indicators refers to topics such as effort and talent, and the non-meritocratic refers to family wealth and networks. The three combinations relies in how these indicators are displayed to the respondent. The first combination corresponds to the group that answered the questions that were sorted by the Perceptions/Preferences dimension. the second combination corresponds to the group in which the questions are displayed following the a topic-sorted way, this means that the effort, talent, rich family and networks questions for perception and preference were displayed together. The last and third group corresponds to a completely randomized display order of the questions.

The rationale of the design relies on the possibility to test how different display modalities could affect the hypothesized factor structure of the scale. On this regard, we conducted the analysis on two stages. On the first stage we tested the hypothesized factor structure on the three groups corresponding to each application modality and the full sample using a Confirmatory Factor Analysis (CFA). On the second stage, we conducted a Multi-group confirmatory factor analysis (MGCFA) using the groups created by the randomization. Furthermore, we explore the possibility of a second order factor structure, in which we tested two models. The first alternative corresponds to a second-order Confirmatory Factor Analysis assuming the Perception/Preference dimension as a second order factor. On the other hand, we tested a model in which we assume that the second order factor structure follows the Meritocratic/Non-meritocratic constructs.

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.Rmd",output_format = "html_document"); browseURL(url = "production/prod_analysis-cfa.html")
```

@@

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(semPlot)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

**Load data**

```{r}
load(file = "input/data/proc/dat01.RData")
load(file = "input/data/proc/dat02.RData")
load(file = "input/data/proc/dat03.RData")
load(file = "input/data/proc/dat04.RData")
```

```{r eval=FALSE, include=FALSE}
data01 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola1.sav",verbose = FALSE)
dat01 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv01"))   %>% na.omit()
dat02 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv02"))   %>% na.omit()
dat03 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv03_p")) %>% na.omit()

@@

dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
dat04 <- dat04 %>% select(starts_with(match = "perc_"),starts_with(match = "pref_"),grupo) %>% na.omit()
```

@@

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| A. Percepción esfuerzo      | Perception effort      |
| B. Percepción talento       | Perception talent      |
| C. Percepción familia rica  | Perception rich family |
| D. Percepción redes         | Perception networks    |
| E. Preferencia esfuerzo     | Preference effort      |
| F. Preferencia talento      | Preference talent      |
| G. Preferencia familia rica | Preference rich family |
| H. Preferencia redes        | Preference networks    |
Table: Mode 01: Fixed order by perception

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw"))
```

```{r correlacion v01}
cor01<-polychoric(dat01)
rownames(cor01$rho) <- c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor01$rho) <- c("(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r}
source(file = "production/prod_polychoric.R")
corr.test(cor01$rho)
sjt.corr(data = cor01$rho,triangle = "lower",digits = 2)
sjt.corr(data = dat01,triangle = "lower",digits = 2,var.labels = " ")

corr <- psych::polychoric(data,  na.rm = TRUE)

@@

```{r}
model01 <- 'perc_merit=~perc_effort+perc_talent
            perc_nmerit=~perc_wpart+perc_netw
            pref_merit=~pref_effort+pref_talent
            pref_nmerit=~pref_wpart+pref_netw'

@@

fit1_o <- cfa(model = model01,data = dat01,
            ordered = c("perc_effort","perc_talent",
                        "perc_wpart","perc_netw",
                        "pref_effort","pref_talent",
                        "pref_wpart","pref_netw"))

@@

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| A. Percepción esfuerzo      | Perception effort      |
| E. Preferencia esfuerzo     | Preference effort      |
| B. Percepción talento       | Perception talent      |
| F. Preferencia talento      | Preference talent      |
| C. Percepción familia rica  | Perception rich family |
| G. Preferencia familia rica | Preference rich family |
| D. Percepción redes         | Perception networks    |
| H. Preferencia redes        | Preference networks    |
Table: Mode 02: Fixed order, by topic.

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort","E. pf.effort","B. pc.talent","F. pf.talent","C. pc.wpart","G. pf.wpart","D. pc.netw","H. pc.netw"))
```

```{r}
cor02<-polychoric(dat02)
rownames(cor02$rho) <-c("A. pc.effort","E. pf.effort","B. pc.talent","F. pf.talent","C. pc.wpart","G. pf.wpart","D. pc.netw","H. pc.netw")
colnames(cor02$rho) <-c("(A)", "(E)","(B)","(F)","(C)","(G)","(D)", "(H)")
corrplot(cor02$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model02 <- 'perc_merit=~perc_effort+perc_talent
            perc_nmerit=~perc_wpart+perc_netw
            pref_merit=~pref_effort+pref_talent
            pref_nmerit=~pref_wpart+pref_netw'

@@

fit2_o <- cfa(model = model02,data = dat02,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart"  ,"perc_netw",
                                                       "pref_effort" ,"pref_talent",
                                                       "pref_wpart"  ,"pref_netw"))

@@

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw"))
```

```{r}
cor03<-polychoric(dat03)
rownames(cor03$rho) <-c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor03$rho) <-c("(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
corrplot(cor03$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~perc_effort+perc_talent
perc_nmerit=~perc_wpart+perc_netw
pref_merit=~pref_effort+pref_talent
pref_nmerit=~pref_wpart+pref_netw'

@@

fit3_o <- cfa(model = model03,data = dat03,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart","perc_netw",
                                                       "pref_effort","pref_talent",
                                                       "pref_wpart","pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

@@

```{r,results='hold'}
model03.tau <- '
perc_merit=~ r1*perc_effort+r1*perc_talent
perc_nmerit=~r2*perc_wpart+ r2*perc_netw
pref_merit=~ r3*pref_effort+r3*pref_talent
pref_nmerit=~r4*pref_wpart+ r4*pref_netw'

@@

fit3_o.tau <- cfa(model = model03.tau,data = dat03,ordered = c("perc_effort","perc_talent",
                                                               "perc_wpart","perc_netw",
                                                               "pref_effort","pref_talent",
                                                               "pref_wpart","pref_netw"), std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c.tau ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o.tau) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

@@

```{r echo=FALSE,results='asis'}
stargazer(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw),
          type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw"))
```

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

# Summary

```{r semPlot, fig.cap="Measurement model PPM-S", fig.height=8, fig.width=12}
model01 <- 'perc_merit=~perc_effort+perc_talent
            perc_nmerit=~perc_wpart+perc_netw
            pref_merit=~pref_effort+pref_talent
            pref_nmerit=~pref_wpart+pref_netw'

plot01 <- cfa(model = model01,data = dat01,estimator="MLR",std.lv=TRUE)

nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception networks",
              "Preference effort","Preference talent","Preference rich family","Preference networks",
              "Percepction meritocratic","Percepction non meritocratic","Preference meritocratic","Preference non meritocratic")

semPaths(plot01,
         style = "lisrel",
         fade=FALSE,
         edge.color = "black",
         nCharNodes = 0,
         curvePivot = FALSE,
         curve = 2,
         rotation = 4,
         layout = "tree3",
         cardinal = "lat cov",
         legend.cex = 0.6,
         label.cex =1,
         reorder = FALSE,
         nodeNames = nodeNames,
         nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"),
         label.font = 6,
         edge.label.font= 1,
         asize = 3, #arrow size
         edge.width =1,
         sizeMan=5,
         sizeLat = 10)
```

## Fit indices wave 01
```{r}
sum_fit<- bind_rows(fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
sum_fit$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fit$est <- c("MLR","DWLS","MLR","DWLS","MLR","DWLS","MLR","DWLS")
sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: fixed order by percepction/preference",
                          "Model 2: fixed order by topic (i.e: effort)",
                          "Model 3: Randomized order",
                          "Model 4: Complete sample"));sumtable01

@@

```{r results='asis'}
stargazer(w02con,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r results='asis'}
stargazer(w02pob,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r results='asis'}
stargazer(w02des,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

@@

```{r}
sum_fitw02<- bind_rows(fitmeasures(fitw02a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02a_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_c)[ c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_o)[ c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],)

sum_fitw02$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fitw02$est <- c("MLR","DWLS","MLR","DWLS","MLR","DWLS","MLR","DWLS")
sum_fitw02 <- select(sum_fitw02,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

kable(sum_fitw02,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 02", col.names = colnames, escape = F) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1,valign = "middle") %>%
  footnote(number = c("Model 1: Control group sample",
                      "Model 2: Poverty treatment condition sample",
                      "Model 3: Inequality treatment condition sample",
                      "Model 4: Complete sample"))
```
